The \frb\ Observing Campaign: Multi-Telescope Radio Burst and Implications for the FRB Population

### 2016-12-19 repeater-vladata.tex
reworking dm changes

\author{D.~Michilli}
\affiliation{Anton Pannekoek Institute for Astronomy, University of Amsterdam, Science Park 904, 1098 XH Amsterdam, The Netherlands}

@@

\subsubsection{Spectra}
\label{sec:spec}
Figure \ref{fig:sgram} shows the dynamic spectra of all nine bursts detected by the VLA. We improved on the initial analysis presented in \citet{LOC} by using a better calibration scheme and optimizing the detection significance over a fine grid of DM ($\Delta \rm{DM}=1 \rm{pc} \rm{cm}^{-3}$). Table \ref{tab:spec} shows the improved burst parameters using this new scheme.

@@

\subsubsection{Dispersion}
The initial VLA detections were made by searching a DM grid that allowed inter-DM sensitivity losses up to roughly 10\% \citep[$\Delta DM=10 \rm{pc} \rm{cm}^{-3}$][]{2003ApJ...596.1142C}. In optimizing detection significance over a fine DM grid, we find optimal DM values range from 552 to 572 pc cm$^{-3}$. However, the uncertainty in the peak DM measurement is defined by the DM sensitivity loss curve and the significance of the burst.

@@

 **Preliminary** Figure \ref{fig:dmmodel} compares the 95\% confidence intervals on the DM for all nine VLA bursts. The DM confidence intervals are not consistent with a single DM, which suggests that there are apparent DM changes between bursts. This change could be caused by intrinsic burst structure or actual changes to the DM column density.

@@

\subsection{FRB Rate}
% cut from gemini paper. TODO: incorporate referee comments on rate scale. Sarah?
Assuming that \frb is from the same population as the other FRBs, the measurement of a distance for the host of \frb allows us to re-evaluate the cosmic volume and event rate per galaxy for the FRB population. The estimated projected FRB rate $R_p$ understates the true rate by a beaming fraction $\Omega_b$ \citep[$\sim$10\%;][]{1998MNRAS.298..625T}.. For a comoving volume $V(z)$ and galaxy number density $\Phi(M)$, the rate per galaxy is $R_{FRB} = R_p \Omega_b /(\Phi(M)V (z))$.

The first such rate estimate was made by \citet{2013Sci...341...53T}, who used the measured DM to estimate a characteristic distance for their sample of 4 FRBs. They assumed that all of the extragalactic component of the DM was caused by the IGM and scaled as $DM\approx z\times1200 \rm{pc} \rm{cm}^{-3}$ \citep{2003ApJ...598L..79I,2004MNRAS.348..999I}. They also calculated the number of galaxies by assuming a characteristic $L_*$ galaxy \citep[corresponding to stellar mass $M_* \approx 1010.66 M$][]{2012MNRAS.421..621B}.

>>>>

\author{D.~Michilli}
\affiliation{ASTRON, Netherlands Institute for Radio Astronomy, Postbus 2, 7990 AA, Dwingeloo, The Netherlands}
\affiliation{Anton Pannekoek Institute for Astronomy, University of Amsterdam, Science Park 904, 1098 XH Amsterdam, The Netherlands}

@@

\subsubsection{Spectra}
\label{sec:spec}
Figure \ref{fig:sgram} shows the dynamic spectra of all nine bursts detected by the VLA. We improved on the initial analysis presented in \citet{LOC} by using a better calibration scheme and optimizing the detection significance over a fine grid of DM ($\Delta \rm{DM}=1 \rm{pc}\ \rm{cm}^{-3}$). Table \ref{tab:spec} shows the improved burst parameters using this new scheme.

@@

\subsubsection{Dispersion}
The initial VLA detections were made by searching a DM grid that allowed inter-DM sensitivity losses up to roughly 10\% \citep[$\Delta DM=10 \rm{pc}\ \rm{cm}^{-3}$][]{2003ApJ...596.1142C}. In optimizing detection significance over a fine DM grid, we find optimal DM values range from 552 to 572 pc cm$^{-3}$. However, the uncertainty in the peak DM measurement is defined by the DM sensitivity loss curve and the significance of the burst.

@@

 **Preliminary** Figure \ref{fig:dmmodel} compares the 95\% confidence intervals on the DM for all nine VLA bursts. The DM confidence intervals {\color{red} are/are not} consistent with a single DM... %, which suggests that there are apparent DM changes between bursts. This change could be caused by intrinsic burst structure or actual changes to the DM column density.

@@

\subsection{FRB Rate}
% cut from gemini paper. TODO: incorporate referee comments on rate scale. Sarah?
Assuming that \frb is from the same population as the other FRBs, the measurement of a distance for the host of \frb allows us to re-evaluate the cosmic volume and event rate per galaxy for the FRB population. The estimated projected FRB rate $R_p$ understates the true rate by a beaming fraction $\Omega_b$ \citep[$\sim$10\%;][]{1998MNRAS.298..625T}.. For a comoving volume $V(z)$ and galaxy number density $\Phi(M)$, the rate per galaxy is $R_{FRB} = R_p /(\Omega_b \Phi(M)V (z))$.

The first such rate estimate was made by \citet{2013Sci...341...53T}, who used the measured DM to estimate a characteristic distance for their sample of 4 FRBs. They assumed that all of the extragalactic component of the DM was caused by the IGM and scaled as $DM\approx z\times1200 \rm{pc}\ \rm{cm}^{-3}$ \citep{2003ApJ...598L..79I,2004MNRAS.348..999I}. They also calculated the number of galaxies by assuming a characteristic $L_*$ galaxy \citep[corresponding to stellar mass $M_* \approx 1010.66 M$][]{2012MNRAS.421..621B}.
